---
title: "Diet 2 Analysis"
author: "Han Yin"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  bookdown::html_document2:
    number_sections: no
    fig_caption: true
    toc: true
    toc_float: true
    toc_depth: 3
    code_folding: hide
    df_print: paged
header-includes:
- \usepackage{graphicx}
- \usepackage{float}
editor_options:
  chunk_output_type: inline
---

```{r setup knit, include=FALSE}
knitr::opts_chunk$set(
	fig.align = "center",
	fig.pos = "H",
	message = FALSE,
	warning = FALSE,
	external = TRUE,
	echo = TRUE
)
```

```{r library and dataset}
library(magrittr)
library(tidyverse)
library(reshape2)
library(fastDummies)

library(ggsci)

library(survival)
library(survminer)

cut_off = 10

rep1 = readxl::read_excel("data/SSMI_DietSwitch.xlsx", sheet = 1) %>% na.omit()
rep2 = readxl::read_excel("data/SSMI_DietSwitch.xlsx", sheet = 2) %>% na.omit()
rep3 = readxl::read_excel("data/SSMI_DietSwitch.xlsx", sheet = 3) %>% na.omit()

df = bind_rows(rep1, rep2, rep3) %>% 
  mutate(Diet = gsub(" ", "", Diet, fixed = TRUE),
         Diet = recode(Diet,
                       "Cornmeal,C,C" = "C/C",
                       "Glucose,G,G" = "G/G",
                       "Cornmeal,G,G" = "C/G",
                       "Glucose,C,C" = "G/C")) %>% 
  filter(Diet %in% c("C/C","G/G","C/G","G/C"),
         Day<=cut_off)
# write.csv(df,"DIET 2 raw.csv")
```

### Raw data plot {.tabset}

Seems good :)  

#### Replicates combined

```{r replicates combined, fig.width=10, fig.height=5}
day_end = df %>% 
  group_by(Population,Diet,Treatment,Sex,Day) %>% 
  summarize(Death = sum(Death), Initial = sum(`Initial density`)) %>% 
  group_by(Population,Diet,Treatment,Sex) %>% 
  mutate(Deaths = cumsum(Death)) %>% 
  ungroup() %>% 
  mutate(surv_per = 1-Deaths/Initial) %>% 
  select(-c(Death,Initial,Deaths))

day_initial = day_end %>% select(-c(Day,surv_per)) %>% 
  unique() %>% 
  mutate(Day=0, surv_per = 1)

goal = bind_rows(day_initial,day_end) %>% 
  ggplot(aes(x=Day, y=surv_per, linetype=Treatment, color=Diet, shape=Sex)) + 
  geom_line() + 
  geom_point() + 
  ylim(0.35,1) +
  labs(linetype="", color="", shape="") +
  theme_minimal()

goal + facet_wrap(~Diet, ncol=4)
```

#### Replicate 1

```{r replicate 1, fig.width=10, fig.height=5}
day_end = df %>% 
  group_by(Replicate,Population,Diet,Treatment,Sex,Day) %>% 
  summarize(Death = sum(Death), Initial = sum(`Initial density`)) %>% 
  group_by(Replicate,Population,Diet,Treatment,Sex) %>% 
  mutate(Deaths = cumsum(Death)) %>% 
  ungroup() %>% 
  mutate(surv_per = 1-Deaths/Initial) %>% 
  select(-c(Death,Initial,Deaths))

day_initial = day_end %>% select(-c(Day,surv_per)) %>% 
  unique() %>% 
  mutate(Day=0, surv_per = 1)

bind_rows(day_initial,day_end) %>% 
  filter(Replicate == 1) %>% 
  ggplot(aes(x=Day, y=surv_per, linetype=Treatment, color=Diet, shape=Sex)) + 
  geom_line() + 
  geom_point() + 
  facet_wrap(Replicate~Diet, ncol=4) +
  ylim(0.35,1) +
  labs(linetype="", color="", shape="") +
  theme_minimal()
```

#### Replicate 2

```{r replicate 2, fig.width=10, fig.height=5}
bind_rows(day_initial,day_end) %>% 
  filter(Replicate == 2) %>% 
  ggplot(aes(x=Day, y=surv_per, linetype=Treatment, color=Diet, shape=Sex)) + 
  geom_line() + 
  geom_point() + 
  facet_wrap(Replicate~Diet, ncol=4) +
  ylim(0.35,1) +
  labs(linetype="", color="", shape="") +
  theme_minimal()
```

#### Replicate 3

```{r replicate 3, fig.width=10, fig.height=5}
bind_rows(day_initial,day_end) %>% 
  filter(Replicate == 3) %>% 
  ggplot(aes(x=Day, y=surv_per, linetype=Treatment, color=Diet, shape=Sex)) + 
  geom_line() + 
  geom_point() + 
  facet_wrap(Replicate~Diet, ncol=4) +
  ylim(0.35,1) +
  labs(linetype="", color="", shape="") +
  theme_minimal()
```

### Data manipulation

```{r death count to status}
n = nrow(df)

# duplicate dead 
dead = df[ rep(c(1:n), df$Death), ] %>% mutate(Death = 1) %>% select(-c(`Initial density`))

# count alive
alive = df %>% 
  group_by(Replicate,Population,Cage_Number,Diet,Treatment,Sex) %>%
  summarise(Deaths = sum(Death), Initial = max(`Initial density`)) %>% 
  ungroup() %>%
  mutate(Alive = Initial - Deaths)

# duplicate alive
n = nrow(alive)
alive = alive[ rep(c(1:n), alive$Alive), ] %>% mutate(Day = cut_off, Death = 0)
alive = alive[c(names(dead))]

# concatenate dead and alive
df = rbind(alive, dead) %>% 
  mutate_at(c("Replicate","Population","Cage_Number","Diet","Treatment","Sex"), function(x) as.factor(x))
```

### Test replicates {.tabset}

Good to go :) 

```{r function to test replicate}
test_replicate = function(diet_type){
  subset = df %>% filter(Diet == diet_type)
  fit = survfit(Surv(Day, Death) ~ Replicate, data = subset)
  # ggsurvplot(fit, surv.median.line = "hv", pval = TRUE)
  pairwise_survdiff(Surv(Day, Death == 1) ~ Replicate, p.adjust.method = "holm", data = subset)
}
```

#### C/C

```{r}
test_replicate("C/C")
```


#### C,G

```{r test replicates for c,g,g}
test_replicate("C/G")
```

#### G, C

```{r test replicates for g,c,c}
test_replicate("G/C")
```

#### G/G
```{r test replicates for g,g,c}
test_replicate("G/G")
```

### Cox model 

#### Goal

```{r}
goal
```

#### 1. Check proportionality

```{r check proportionality, echo=TRUE}
mod = coxph(Surv(Day, Death) ~ Treatment + Diet + Sex, data = df)
cox.zph(mod)
```

#### 2. Potential splittting point {.tabset}

##### Treatment

```{r strata at Treatment, fig.width=4, fig.height=4}
mod = coxph(Surv(Day, Death) ~ strata(Treatment) + Diet + Sex, data = df)
pred = survfit(mod)
plot(pred, lty = 1:2, col = c("red","blue"))
```

##### Diet

```{r strata at Diet, fig.width=4, fig.height=4}
mod = coxph(Surv(Day, Death) ~ Treatment + strata(Diet) + Sex, data = df)
pred = survfit(mod)
plot(pred, lty = 1:2, col = c("red","green","blue","orange","black"))
```

##### Sex

```{r strata at Sex, fig.width=4, fig.height=4}
mod = coxph(Surv(Day, Death) ~ Treatment + Diet + strata(Sex), data = df)
pred = survfit(mod)
plot(pred, lty = 1:2, col = c("red","blue"))
```

#### 3. Convert to time-dependent

```{r choose time points}
# split the data into intervals
a1 = 3; a2 = 8; 
split_time = c(a1,a2)
df2 = survSplit(df, cut=split_time, end="Day", event="Death", start="Start") %>%
  mutate(Diet = gsub(",", "_", Diet)) %>%
  mutate(gt1 = (Start==0)+0, gt2 = (Start==a1)+0, gt3 = (Start==a2)+0,
         Fungal = (Treatment=="Fungal")+0, Female = (Sex=="F")+0) %>% 
  dummy_cols("Diet")
  
# build time-dependent model
mod = coxph(Surv(Start, Day, Death) ~ 
              
              Fungal:gt1 + Fungal:gt2 + Fungal:gt3 +
              Female:gt1 + Female:gt2 + Female:gt3 + 
              
              `Diet_G/G`:gt1 + `Diet_G/G`:gt2 + `Diet_G/G`:gt3 +
              `Diet_G/C`:gt1 + `Diet_G/C`:gt2 + `Diet_G C`:gt3 +
              `Diet_C/G`:gt1 + `Diet_C/G`:gt2 + `Diet_C/G`:gt3 +
              
              Fungal:Female:gt1 + Fungal:Female:gt2 + Fungal:Female:gt3 +
              
              `Diet_G/G`:Fungal:gt1 + `Diet_G/G`:Fungal:gt2 + `Diet_G/G`:Fungal:gt3 +
              `Diet_G/C`:Fungal:gt1 + `Diet_G/C`:Fungal:gt2 + `Diet_G/C`:Fungal:gt3 +
              `Diet_C/G`:Fungal:gt1 + `Diet_C/G`:Fungal:gt2 + `Diet_C/G`:Fungal:gt3 +
            
              `Diet_G/G`:Female:Fungal:gt1 + `Diet_G/G`:Female:Fungal:gt2 + `Diet_G/G`:Female:Fungal:gt3 +
              `Diet_C/G`:Female:Fungal:gt1 + `Diet_C/G`:Female:Fungal:gt2 + `Diet_C/G`:Female:Fungal:gt3,
              
              df2)

# test assumptions again
# cox.zph(mod)
# cox.zph(mod, transform = log)
# summary(mod)
extractAIC(mod)
```

```{r}
a1 = 2; a2 = 4; a3 = 8
split_time = c(a1,a2,a3)
df2 = survSplit(df, cut=split_time, end="Day", event="Death", start="Start") %>%
  mutate(Diet = gsub(",", "_", Diet)) %>%
  mutate(gt1 = (Start==0)+0, gt2 = (Start==a1)+0, gt3 = (Start==a2)+0, gt4 = (Start==a3)+0,
         Fungal = (Treatment=="Fungal")+0, Female = (Sex=="F")+0) %>% 
  dummy_cols("Diet")
  
# build time-dependent model
mod = coxph(Surv(Start, Day, Death) ~ 
              
              Fungal:gt1 + Fungal:gt2 + Fungal:gt3 + Fungal:gt4 +
              Female:gt1 + Female:gt2 + Female:gt3 + Female:gt4 + 
              
              `Diet_G/G`:gt1 + `Diet_G/G`:gt2 + `Diet_G/G`:gt3 + `Diet_G/G`:gt4 +
              `Diet_G/C`:gt1 + `Diet_G/C`:gt2 + `Diet_G C`:gt3 + `Diet_G C`:gt4 + 
              `Diet_C/G`:gt1 + `Diet_C/G`:gt2 + `Diet_C/G`:gt3 + `Diet_C/G`:gt4 +
              
              Fungal:Female:gt1 + Fungal:Female:gt2 + Fungal:Female:gt3 + Fungal:Female:gt4 +
              
              `Diet_G/G`:Fungal:gt1 + `Diet_G/G`:Fungal:gt2 + `Diet_G/G`:Fungal:gt3 + `Diet_G/G`:Fungal:gt4 +
              `Diet_G/C`:Fungal:gt1 + `Diet_G/C`:Fungal:gt2 + `Diet_G/C`:Fungal:gt3 + `Diet_G/C`:Fungal:gt4 +
              `Diet_C/G`:Fungal:gt1 + `Diet_C/G`:Fungal:gt2 + `Diet_C/G`:Fungal:gt3 + `Diet_C/G`:Fungal:gt4 +
            
              `Diet_G/G`:Female:Fungal:gt1 + `Diet_G/G`:Female:Fungal:gt2 + `Diet_G/G`:Female:Fungal:gt3 +
              `Diet_G/G`:Female:Fungal:gt4 +
              `Diet_C/G`:Female:Fungal:gt1 + `Diet_C/G`:Female:Fungal:gt2 + `Diet_C/G`:Female:Fungal:gt3 +
              `Diet_C/G`:Female:Fungal:gt4,
              
              df2)

# test assumptions again
# cox.zph(mod)
# cox.zph(mod, transform = log)
# summary(mod)
extractAIC(mod)
```



#### 4. Table of Hazard Ratios

```{r}
beta = coef(mod)
diff = c(1,0,0, # fungal
         0,0,0, # female
         
         0,0,0, # g_g
         0,0,0, # g_c
         1,0,0, # c_g

         1,0,0, # female fungal
         
         0,0,0, # g_g fungal
         0,0,0, # g_c fungal
         1,0,0, # c_g fungal
    
         0,0,0, # female g_g fungal
         1,0,0  # female c_g fungal
         )

t_obs = (beta%*%diff) / sqrt(t(diff) %*% vcov(mod) %*% diff)
c(exp(beta%*%diff),
2*(1-pt(abs(t_obs), length(beta))))
```

#### 5. Calculate survival probabilities

```{r}
get_interaction = function(data){
  data %>% 
    mutate(
      t1_fun=Fungal*gt1, t2_fun=Fungal*gt2, t3_fun=Fungal*gt3,
      t1_fem=Female*gt1, t2_fem=Female*gt2, t3_fem=Female*gt3,
 
      t1_gg=`Diet_G/G`*gt1, t2_gg=`Diet_G/G`*gt2, t3_gg=`Diet_G/G`*gt3,
      t1_gc=`Diet_G/C`*gt1, t2_gc=`Diet_G/C`*gt2, t3_gc=`Diet_G/C`*gt3, 
      t1_cg=`Diet_C/G`*gt1, t2_cg=`Diet_C/G`*gt2, t3_cg=`Diet_C/G`*gt3, 
      
      ff1=Fungal*Female*gt1, ff2=Fungal*Female*gt2, ff3=Fungal*Female*gt3, 
    
      f1_gg=Fungal*`Diet_G/G`*gt1, f2_gg=Fungal*`Diet_G/G`*gt2, f3_gg=Fungal*`Diet_G/G`*gt3,
      f1_gc=Fungal*`Diet_G/C`*gt1, f2_gc=Fungal*`Diet_G/C`*gt2, f3_gc=Fungal*`Diet_G/C`*gt3, 
      f1_cg=Fungal*`Diet_C/G`*gt1, f2_cg=Fungal*`Diet_C/G`*gt2, f3_cg=Fungal*`Diet_C/G`*gt3, 
    
      ff1_gc=Fungal*Female*`Diet_G/C`*gt1, ff2_gc=Fungal*Female*`Diet_G/C`*gt2, ff3_gc=Fungal*Female*`Diet_G/C`*gt3, 
      ff1_cg=Fungal*Female*`Diet_C/G`*gt1, ff2_cg=Fungal*Female*`Diet_C/G`*gt2, ff3_cg=Fungal*Female*`Diet_C/G`*gt3, 
  )
}

get_time_data = function(data){
  data = survSplit(data, cut=split_time, end="Day", event="Death", start="Start") %>% 
    mutate(Diet = gsub(",", "_", Diet),
           gt1=(Start==0)+0, gt2=(Start==a1)+0, gt3=(Start==a2)+0, 
           Fungal = (Treatment=="Fungal")+0, Female = (Sex=="F")+0) %>% 
    dummy_cols("Diet") %>% get_interaction()
  return(data)
}

category = ungroup(df) %>% select(Treatment,Sex,Diet) %>% unique() %>% set_rownames(NULL) %>%
   mutate(Diet = gsub(",", "_", Diet), Fungal = (Treatment=="Fungal")+0, Female = (Sex=="F")+0) %>% 
  dummy_cols("Diet")

time_intervals = data.frame(Start=c(0,a1,a2), Day=c(a1,a2,12), 
                            gt1=c(1,0,0), gt2=c(0,1,0), gt3=c(0,0,1),
                            Death=0)

pred_surv = function(data){
  mod = coxph(Surv(Start, Day, Death) ~ 
                t1_fun + t2_fun + t3_fun + 
                t1_fem + t2_fem + t3_fem +
                
                t1_gg + t2_gg + t3_gg +
                t1_gc + t2_gc + t3_gc + 
                t1_cg + t2_cg + t3_cg +
                
                ff1 + ff2 + ff3 + 
                
                f1_gg + f2_gg + f3_gg +
                f1_gc + f2_gc + f3_gc + 
                f1_cg + f2_cg + f3_cg +
                
                ff1_gc + ff2_gc + ff3_gc + 
                ff1_cg + ff2_cg + ff3_cg,
              data = get_time_data(data))
  
  surv = c()
  for (i in 1:nrow(category)){
    test = category[rep(i,nrow(time_intervals)),] %>%
      bind_cols(time_intervals) %>%
      get_interaction()
    time = summary(survfit(mod, newdata = test, individual = TRUE))$time
    insert = setdiff(1:12, time)
    time = c(time, insert)
    est = c(1, summary(survfit(mod, newdata = test, individual = TRUE))$surv,
            rep(NA, length(insert)))
    surv_i = data.frame(category[i,], est, day = c(0,time)) %>% arrange(day)
    surv = rbind(surv, surv_i)
  }
  return(surv)
}

est = pred_surv(df) 
```

#### 6. Bootstrap confidence intervals

```{r bootstrap ci}
B = 200
bound = 0.95

# function to extract bounds
ci_calculator = function(data){
  ci = data.frame(lower = as.numeric(), upper = as.numeric())
  for (i in 1:(max(data$Day)+1)) {
    ci[i,1] = quantile(data$est[data$Day == (i-1)], (1-bound)/2, na.rm = TRUE)
    ci[i,2] = quantile(data$est[data$Day == (i-1)], (1+bound)/2, na.rm = TRUE)
  }
  return(ci)
}

dff = df %>% mutate(Diet = gsub(",", "_", Diet), Fungal = (Treatment=="Fungal")+0, Female = (Sex=="F")+0) %>% 
  dummy_cols("Diet")

# repeat B times
dummy = c()
for (i in 1:B){
  dummy_i = c()
  for (j in 1:nrow(category)){
    dummy_ij = merge(dff, category[j,])
    a = nrow(dummy_ij)
    rows_to_take = sample(a, a, replace = TRUE)
    dummy_i = rbind(dummy_i, dummy_ij[rows_to_take,])
    }
  dummy_i = pred_surv(dummy_i)
  dummy = bind_rows(dummy, dummy_i)
}

# get confidence intervals
survs = c()
for (i in 1:nrow(category)){
  ci = merge(dummy, category[i,]) %>% mutate(Day=day) %>% ci_calculator()
  surv = merge(est, category[i,]) %>% arrange(day)
  surv = cbind(surv, ci)
  survs = rbind(survs, surv)
}

# recode labels
df_plot = survs %>% 
  mutate(Treatment = ifelse(Fungal==1, "Fungal","Control"), 
         Sex = ifelse(Female==1, "Female","Male"))
# write.csv(df_plot, "DIET 2 bootstrap.csv")
```

#### Results {.tabset}

##### raw

```{r}
goal + labs(y="Survival Percent") + 
  facet_wrap(Treatment~Sex)
```


##### model


```{r}
df_plot %>% 
  na.omit() %>% 
  ggplot(aes(x=day, y=est, ymin=lower, ymax=upper, linetype=Treatment, color=Diet, shape=Sex)) +
  geom_line() + 
  geom_point() +
  # geom_errorbar(width=0.3, alpha=0.7) +
  ylim(0.35,1) +
  scale_linetype_manual(values = c("Control"="dashed","Fungal"="solid")) +
  labs(linetype="", color="", shape="", y="Survival Probabilities") +
  theme_minimal() + 
  facet_wrap(~Sex)
```





